---
title: "crimenes_250_50m"
author: "Laura.w"
date: "2/20/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}


```
```{r}
library(readxl)
library(readr)

data_250 <- read_xlsx('C://Users//LW//Box//Mexico City 2020//data//buffer_250_crime1_TableToExcel.xlsx')

data_250
```


##Crimes within a 250m radius

Summary of crimes within a 250 radius of any school
```{r}
data(data_250, package = "DMwR2")
summary(data_250)
summary(data_250$Join_Count)
```
###We can review the vairance, standard deviation, and inter-quartile ranges:
```{r}
#variance
var(data_250$Join_Count)

#standard deviation
sd(data_250$Join_Count)

#inter-quartile range
quantile(data_250$Join_Count)


quantile(data_250$Join_Count, probs=c(0.2, 0.8))
```

## Joint Count Distribution

Our histogram is skewed to the lower end of the crime numbers, with most areas experiencing under 150 crimes.

When we look at the bandwith a little closer we can see that most areas with a 250 radius aruond a school have between 25 and 75 crimes on average, with 50 crimes 
```{r}

library(ggplot2)

hist(data_250$Join_Count)

ggplot(data_250) +
    geom_histogram(aes(x = data_250$Join_Count),
                   binwidth = 25, fill = "blue", color = "black")
```

And look at the frequency of crimes
```{r}
freq <- table(data_250$Join_Count)
barplot(freq, main="Frequency of crimes within a 250m radius")
```

```{r}
boxplot(data_250$Join_Count)


```

```{r}


```

```{r}
ggplot(data_250, aes(x=delito, y=Join_Count)) + geom_point()+ggtitle("Relationship crime and count")


```

```{r}
freq <- table(data_250$delito)
barplot(freq, main="Frequency of crimes within a 50m radius")
```




```{r}
library(readxl)
table(data_250$Join_Count, data_250$nombre)

```

```{r}
library(dplyr)

missing.value.rows <- filter(data_250, !complete.cases(data_250)) 
missing.value.rows


apply(data_250, 1, function(x) sum(is.na(x)))

sort(apply(data_250, 2, function(x) sum(is.na(x))))

```

```{r}
dfdata_250 <- data.frame(data_250)

fctdelt_250 <- as.factor(data_250$delito)

fctnom_250 <- as.factor(data_250$nombre)


```

```{r}
table2 <- table(data_250$delito, data_250$nombre, data_250$Join_Count)
table2

```

```{r}
library(lattice)
densityplot(~ fctnom_250, group = fctdelt_250, data = data_250, auto.key = TRUE)

ggplot(data_250) + geom_density(aes(x = fctnom_250))
ggplot(data_250) + geom_density(aes(x = data_250$Join_Count))
ggplot(data_250) + geom_density(aes(x = fctdelt_250))


```

```{r}
densityplot(~ fctnom_250, group = fctdelt_250, data = data_250, auto.key = TRUE)

```