---
title: "conavel_review"
author: "Laura.w"
date: "4/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reviewing Conavel .shp files

I found these files through Conavel's search withoug descriptions. They won't open in ArcGis (potential language barrier), so I thought I'd take a look here.

There still isn't much to go by other than the acromyms, A, E, L, M, SIA, SIL, SIP, and T. I couldn't find much help on Conavel's website, or maybe I didn't exactly know where to look. Some look like transportation routes and cites for public/social resources.

Next steps are to look through other data, cdmx.gob & inegi, to see if I can connect the dots. 
 - Most of the information is taken from INEGI so that's a good sign.
 - Most of the data is from 10 years ago, so might not be what we're looking for.

```{r}
library(sf)
library(ggplot2)

```


```{r}
conavelA <- st_read("C://Users//LW//Desktop//conavel1//080370001A.shp")
conavelA
```

```{r}
ggplot() + geom_sf(data=conavelA) + ggtitle("conavelA") + coord_sf()

```

```{r}
conavelCA <- st_read("C://Users//LW//Desktop//conavel1//080370001CA.shp")
conavelCA
ggplot() + geom_sf(data=conavelCA) + ggtitle("conavelCA") + coord_sf()

```


```{r}
conavelE <- st_read("C://Users//LW//Desktop//conavel1//080370001E.shp")
conavelCA

ggplot() + geom_sf(data=conavelE) + ggtitle("conavelE") + coord_sf()

```


```{r}
conavelL <- st_read("C://Users//LW//Desktop//conavel1//080370001L.shp")
conavelL
ggplot() + geom_sf(data=conavelL) + ggtitle("conavelL") + coord_sf()

```

```{r}
conavelM <- st_read("C://Users//LW//Desktop//conavel1//080370001M.shp")
conavelM
ggplot() + geom_sf(data=conavelM) + ggtitle("conavelM") + coord_sf()

```

```{r}
conavelSIA <- st_read("C://Users//LW//Desktop//conavel1//080370001SIA.shp")
conavelM
ggplot() + geom_sf(data=conavelSIA) + ggtitle("conavelSIA") + coord_sf()

```

```{r}
conavelSIP <- st_read("C://Users//LW//Desktop//conavel1//080370001SIP.shp")
conavelSIP
ggplot() + geom_sf(data=conavelSIP) + ggtitle("conavelSIP") + coord_sf()

```

```{r}
conavelSIL <- st_read("C://Users//LW//Desktop//conavel1//080370001SIL.shp")
conavelSIL
ggplot() + geom_sf(data=conavelSIL) + ggtitle("conavelSIL") + coord_sf()

```

```{r}
conavelT <- st_read("C://Users//LW//Desktop//conavel1//080370001T.shp")
conavelT
ggplot() + geom_sf(data=conavelT) + ggtitle("conavelT") + coord_sf()

```

```{r}
conavel2A <- st_read("C://Users//LW//Desktop//conavel2//020010001A.shp")
conavel2A
ggplot() + geom_sf(data=conavel2A) + ggtitle("conavel2A") + coord_sf()

```