---
title: "Region Comparisons"
author: "Laura.w"
date: "2/25/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


```{r}
library(readxl)

library(readr)


data_250 <- read_xlsx('C://Users//LW//Box//Mexico City 2020//data//buffer_250_crime1_TableToExcel.xlsx')

data_150 <- read_xlsx('C://Users//LW//Box//Mexico City 2020//data//buffer_150_crime2.xlsx')

data_100 <- read_xlsx('C://Users//LW//Box//Mexico City 2020//data//buffer_100_crime2_TableToExcel.xlsx')


```


```{r}

library(ggplot2)

ggplot(data_250) +
    geom_histogram(aes(x = data_250$Join_Count),
                binwidth = 25, fill = "blue", color = "black") + theme_minimal(14) + scale_x_continuous(breaks=seq(0,800,100)) + labs(x = "Crime within a 250m radius", y = "Schools")

summary(data_250$Join_Count)


```

```{r}


ggplot(data_150) +
    geom_histogram(aes(x = data_150$Join_Count),
                binwidth = 20, fill = "orange", color = "black") + theme_minimal(14) + scale_x_continuous(breaks=seq(0,500,50)) + labs(x = "Crime within a 150m radius", y = "Schools")

summary(data_150$Join_Count)

```

```{r}
ggplot(data_100) +
    geom_histogram(aes(x = data_100$Join_Count),
                binwidth = 10, fill = "green", color = "black") + theme_minimal(14) + scale_x_continuous(breaks=seq(0,300,20)) + labs(x = "Crime within a 100m radius", y = "Schools")

summary(data_100$Join_Count)

```

The overall number of crime lowers as the radius around the school lowers. 
For example, in a radius of 100m, the maximum number of crimes commited was 232 with an average of 11.28 crimes in the region overall. 

For a radius of 150m, the maximum number of crimes commited was 468 with an average of 26 crimes in the region overall.

Lastly, for a radius of 250m, the maximum number of crimes commited was 691 with an average of 68 crimes throughout the region.

Next steps:
Locate regions (schools) with top crime counts and review from there.

